Sleep Quality Estimation using Raw Data from Thigh-Mounted Accelerometers during Free Living Conditions

### 2023-02-23 presentation/index.qmd
Update README.md
95% CI and mixed effects LOA+bias on plots

---
title: "Sleep Quality Estimation using Thigh-Mounted Accelerometer Data in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

## Background {.scrollable transition="convex"}

@@

## But Esben, what about them sleep stages!?

@@

## Exclusion Criteria {transition="fade" .H2}

@@

## Features {transition="fade" .smaller}

@@

## Human Circadian Clock {.smaller transition="convex"}

@@

## Circadian Proxy Features {.smaller transition="convex"}

@@

## building Models {.smaller transition="convex"}

@@

## Results {transition="fade"}

@@

@@

@@

## ROC Curves {.smaller transition="fade"}

@@

## Lots of Metrics {.smaller transition="zoom" .H2}

@@

## Bland-Altman Plots {.smaller transition="fade"}

@@

```{r}
#| echo: false
source(here::here("presentation/code/plot_ba.R"))
plots$decision_tree[[1]]

plots$decision_tree[[2]]

plots$decision_tree[[3]]

plots$decision_tree[[4]]

plots$decision_tree[[5]]
```

@@

```{r}
plots$logistic_regression[[1]]

plots$logistic_regression[[2]]

plots$logistic_regression[[3]]

plots$logistic_regression[[4]]

plots$logistic_regression[[5]]
```

@@

```{r}
plots$xgboost[[1]]

plots$xgboost[[2]]

plots$xgboost[[3]]

plots$xgboost[[4]]

plots$xgboost[[5]]
```

```{r}
plots$neural_net[[1]]

plots$neural_net[[2]]

plots$neural_net[[3]]

plots$neural_net[[4]]

plots$neural_net[[5]]
```

@@

## Bland-Altman Analysis {.smaller transition="fade" .H2}

@@

## In-bed classification flow {.smaller transition="zoom" .H2}

@@

## Sleep classification flow {.smaller transition="zoom" .H2}

@@

## Discussion {.smaller transition="zoom"}

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.

>>>>

---
title: "Sleep Quality Estimation using Raw Data from Thigh-Mounted Accelerometers during Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

## Background {transition="convex"}

@@

## But Esben, what about them sleep stages!? {transition="convex"}

@@

## Exclusion Criteria {transition="convex" .H2}

@@

## Features {transition="convex" .H2}

@@

## Human Circadian Clock {transition="convex"}

@@

## Circadian Proxy Features {transition="convex"}

@@

## building Models {transition="convex"}

@@

## Results {transition="convex" .H2}

@@

### Epoch-Based

@@

### Summarized across nights {.H3}

@@

## ROC Curves {transition="convex"}

@@

## Lots of Metrics {transition="convex" .H2}

@@

## Bland-Altman Plots {transition="convex"}

@@

```{r}
#| echo: false
source(here::here("presentation/code/plot_ba.R"))

dc_plots[[1]]

dc_plots[[2]]

dc_plots[[3]]

dc_plots[[4]]

dc_plots[[5]]
```

@@

```{r}
lr_plots[[1]]

lr_plots[[2]]

lr_plots[[3]]

lr_plots[[4]]

lr_plots[[5]]
```

```{r}
nn_plots[[1]]

nn_plots[[2]]

nn_plots[[3]]

nn_plots[[4]]

nn_plots[[5]]
```

@@

```{r}
xg_plots[[1]]

xg_plots[[2]]

xg_plots[[3]]

xg_plots[[4]]

xg_plots[[5]]
```

@@

## Bland-Altman Analysis {transition="convex" .H2}

@@

## In-bed classification flow {transition="convex" .H2}

@@

## Sleep classification flow {transition="convex" .H2}

@@

## Discussion {transition="convex"}

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
- multiclass vs multilabel classification
